---
title: "Overall Instructions"
format: html
editor: visual
---

## Update the data files 

The state will have available [research files.](https://caaspp-elpac-preview.ets.org/caaspp/ResearchFileListSB?ps=true&lstTestYear=2022&lstTestType=B&lstCounty=27&lstDistrict=00000#dl)

Download the version with All Student Groups and caret delimited.  it will be about 80MB.  

Updated the SQL_setup project and execute. 
Likely only need to put the file in the correct directory (data > caaspp).
If necessary, in *create-tables.R* modify around line 635 to make sure it reads all the files.  

Push the new file to the SQL Server with the **split_for_sql()** function.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
